Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
spacing
wording
cleanup

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}

@@

\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
%\newcommand{\blue}[1]{}
%\newcommand{\red}[1]{}
%\newcommand{\green}[1]{}

@@

% We no longer use \terms command
%\terms{Theory}

@@

In summary, this paper makes the following original contributions.
%
\begin{itemize}

@@

\end{itemize}

@@

A discrete-time dynamical system is said to be Bounded-Input and
Bounded-Output (BIBO) stable if bounded inputs necessarily result in bounded
outputs.  This condition holds true over an LTI model if and only if every
pole of its transfer function lies inside the unit circle \cite{Astrom08}. 
Analyzing Eq.~\eqref{eq:outputfunctions}, the following proposition provides
conditions for the BIBO stability of the system in
Figure~\ref{fig:sampledsystem}, with regards to the exogenous signals
$R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded (in particular, the
bound on the quantization noise is given by Assumption~\ref{whitenoise}).
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and
uncertain discrete model of the plant
from~\eqref{eq:coefficients}, \eqref{eq:delta_coefficients}
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
\end{equation}
\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

The {\sc verify} phase considers two aspects of soundness.  The first stage
ensures that no counterexample plant with an unstable closed loop exists
over finite-precision arithmetic.  Since the actual plant uses reals, we
need to ensure we do not miss a counterexample because of rounding errors. 
For this reason, the second verification stage uses an overapproximation
with interval arithmetic with outward rounding. Thus, the first verification
stage underapproximates and is used to generate counterexamples, and the
second stage overapproximates and provides proof that no counterexample
exists.

@@

Researchers in formal verification of control systems have studied various
effects of discretizing the dynamics, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics \cite{Anta:2010:AVC:1879021.1879024} 
with the goal to either verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} 
given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focuses on finding a correct
variant of a known controller, looking for optimal parameter
representations using FWL, but ignore the effects of rounding errors due to
issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.  If~the error of the
implementation is lower than this tolerance level, then the verification is
successful.

@@

%In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a control software verification framework for gas turbine engines.

>>>>

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}
\usepackage{mdwlist}

@@

\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\green}[1]{{\color{green}#1}}

@@

@@

In summary, this paper makes the following original contributions.
%
\begin{itemize*}

@@

\end{itemize*}

@@

A discrete-time dynamical system is said to be Bounded-Input and
Bounded-Output (BIBO) stable if bounded inputs necessarily result in bounded
outputs.  This condition holds true over an LTI model if and only if every
pole of its transfer function lies inside the unit circle \cite{Astrom08}. 
Analyzing Eq.~\eqref{eq:outputfunctions}, the following proposition provides
conditions for the BIBO stability of the system in
Figure~\ref{fig:sampledsystem}, with regards to the exogenous signals
$R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded (in particular, the
bound on the quantization noise is given by Assumption~\ref{whitenoise}).
%
\begin{myprop}{\cite{Bessa16,fadali}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and
uncertain discrete model of the plant
from~\eqref{eq:coefficients}, \eqref{eq:delta_coefficients}
%
$$
\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize*}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
\end{equation}
\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize*}
\end{myprop}

@@

The {\sc verify} phase has two stages.  The first stage ensures that no
counterexample plant with an unstable closed loop exists over
finite-precision arithmetic.  Since the actual plant uses reals, we need to
ensure we do not miss a counterexample because of rounding errors.  For this
reason, the second verification stage uses an overapproximation with
interval arithmetic with outward rounding.  Thus, the first verification
stage underapproximates and is used to generate counterexamples, and the
second stage overapproximates and provides proof that no counterexample
exists.

@@

Various effects of discretizing dynamics, including delayed
response~\cite{Duggirala2015} and Finite Word Length (FWL)
semantics~\cite{Anta:2010:AVC:1879021.1879024} have been studied, with the
goal to either verify~\cite{daes20161} or to
optimize~\cite{oudjida2014design} given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focuses on finding a correct
variant of a known controller, looking for optimal parameter representations
using FWL, but ignore the effects of rounding errors due to issues of
mathematical tractability.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of existing code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  If~the error of the implementation is lower than this
tolerance level, then the verification is successful.

@@
